visitation_bias

### 2021-07-15 code/ms2_nullmodels.Rmd
revision

## 2.1 Observed vs. null predictions
```{r}
# Species-wise
ggplot(null_tab1, aes(Observed, ktype)) +
  geom_segment(aes(y = ktype, yend = ktype, 
                   x = Lower.99.CL, xend = Upper.99.CL), 
               color = "gray40", inherit.aes = FALSE) +
  geom_point(aes(color = Test)) +
  facet_wrap(~fct_rev(bb.sp)) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(values = c("gray40", "#F8766D", "#00B6EB")) +
  labs(x = "Mean proportional visitation", y = "Floral morphotype", color = "Test (p < 0.01)") +
  theme_light()

@@

@@

## 2.2 Overall bias by morphotype
```{r}
null_model_overall<- ggplot(null_tab1, aes(ktype, preference)) +
  #geom_violin(fill = "gray70", color = "white", draw_quantiles = c(0.25, 0.5, 0.75)) +
  geom_boxplot(fill = NA, color = "black", outlier.shape = 4, size = 0.35) +
  geom_jitter(aes(color = Test), width = 0.3, alpha = 0.6) +
  theme_light(10) +
  scale_color_manual(values = c("gray40", "#F8766D", "#00B6EB")) +
  labs(x = "Floral morphotype",
       y = "Selectivity")

@@

raw_visits_overall <- ggplot(visitation_prop, aes(ktype, mean.prop.visits)) +
  geom_boxplot(fill = NA, color = "black", outlier.shape = 4, size = 0.35) +
  geom_jitter(width = 0.3, alpha = 0.5, color = "gray40") +
  theme_light(10) +
  labs(x = "Floral morphotype",
       y = "Mean proportional visitation")

>>>>

## 2.1 Observed vs. null predictions
```{r}
# Species-wise
ggplot(null_tab1, aes(Observed, ktype)) +
  geom_segment(aes(y = ktype, yend = ktype, 
                   x = Lower.99.CL, xend = Upper.99.CL), 
               color = "gray40", inherit.aes = FALSE) +
  geom_point(aes(color = Test)) +
  facet_wrap(~fct_rev(bb.sp)) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(values = c("gray40", "#F8766D", "#00B6EB")) +
  labs(x = "Mean visitation rate", y = "Floral morphotype", color = "Test (p < 0.01)") +
  theme_light()

@@

# Species-wise (3-col)
ggplot(null_tab1, aes(Observed, ktype)) +
  geom_segment(aes(y = ktype, yend = ktype, 
                   x = Lower.99.CL, xend = Upper.99.CL), 
               color = "gray40", inherit.aes = FALSE) +
  geom_point(aes(color = Test)) +
  facet_wrap(~fct_rev(bb.sp), ncol = 3) +
  scale_y_discrete(limits = rev) +
  scale_color_manual(values = c("gray40", "#F8766D", "#00B6EB")) +
  labs(x = "Mean visitation rate", y = "Floral morphotype", color = "Test (p < 0.01)") +
  theme_light()

ggsave("../ms_2/figures/null_model_spwise_preference_3col.pdf", height = 6, width = 5)

@@

## 2.2 Overall bias by morphotype
```{r}
null_model_overall<- ggplot(null_tab1, aes(ktype, preference)) +
  #geom_violin(fill = "gray70", color = "white", draw_quantiles = c(0.25, 0.5, 0.75)) +
  geom_boxplot(fill = NA, color = "black", outlier.shape = NA, size = 0.35) +
  geom_jitter(aes(color = Test), width = 0.3, alpha = 0.6) +
  theme_light(10) +
  scale_color_manual(values = c("gray40", "#F8766D", "#00B6EB")) +
  labs(x = "Floral morphotype",
       y = "Selectivity")

@@

raw_visits_overall <- ggplot(visitation_prop, aes(ktype, mean.prop.visits)) +
  geom_boxplot(fill = NA, color = "black", outlier.shape = NA, size = 0.35) +
  geom_jitter(width = 0.3, alpha = 0.5, color = "gray40") +
  theme_light(10) +
  labs(x = "Floral morphotype",
       y = "Mean proportional visitation")
